\title{Introduction}
Welcome to a brief introduction to Madagascar.  The purpose of this document is to teach new users how to use the powerful tools in Madagascar to: process data, produce reproducible scripts and construct reproducible documents.  
To gradually introduce you to Madagascar, we have created a series of tutorials that are targeted to distinct audiences, and designed to make you an experienced Madagascar user in a short-time period.  The tutorials are divided into three main categories (divided by interest):
\begin{itemize}
    \item Users - learn about Madagascar, how to use the processing programs, and build scripts.
    \item Authors - learn how to build reproducible documents using Madagascar.
    \item Developers - build new Madagascar programs that add additional functionality to Madagascar.
\end{itemize}
Each category is further subdivided into individual tutorials that individuals are expected to complete before moving on to the other tutorials in that section.  Failing to follow the order may make other tutorials seem incomplete or confusing, so please try and follow the order.  Additionally, the Authors and Developers tutorials depend on the knowledge obtained in the Users tutorials, so please complete the Users tutorials first!

Each tutorial is designed to be completed in a short period of time (less than 30 minutes each).  Additionally, each tutorial has hands on examples that you should be able to reproduce on your computer as you go along with the tutorials.  Most tutorials will use scripts that you can edit, modify, or play with to further gain experience and understanding.  By the end of the tutorial series, you should be able to use all of the tools inside of Madagascar.  Please note that this tutorial series does not explicitly show you how to process certain types of data, or perform common data processing operations (e.g. cmp semblance picking, time-migration,etc.).  Additional tutorials on those specific subjects will be added over time.  The purpose of this document is only to familiarize you with the Madagascar framework in a general sense.

Before you go on, here are some notes on notation:
\begin{itemize}
    \item important names, or program names are usually bold in the text.  For example: \textbf{sfwindow}
    \item code snippets are always in the following formatting: \begin{verbatim} sfwindow \end{verbatim}
\end{itemize}
